Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-09 paper/paper.tex
Changes to Appendix in the LaTeX document.

\begin{appendices}
\chapter{A} \label{a}
In this appendix we will show in detail the calculation of the boundary of a shadow cast by a sphere by a point light source. The shadow is cast on the z=0 plane. On the z-axis the sphere is strictly between the light and the plane. We are given the location of the 
\end{appendices}

>>>>

\begin{appendices}
\chapter{A} \label{a}

In this appendix we will show in detail the calculation of the boundary of a shadow cast by a sphere by a point light source. The shadow is cast on the z=0 plane. On the z-axis the sphere is strictly between the light and the plane. We are given $\vec{l}$, the location of the point light source, $\vec{c}$, the center of the sphere, and $r$, its radius.

The first step is to derive the equation of the shadow cone. A generic point on the cone will be denoted by $\vec{x}$. The axis of the cone passes through $\vec{l}$ and through $\vec{c}$. The defining property of $\vec{x}$ is 
\begin{equation}\label{xproperty}
\|orth_{\vec{c}-\vec{l}} (\vec{x} - \vec{l})\| = \|proj_{\vec{c}-\vec{l}} (\vec{x} - \vec{l})\| \cdot k
\end{equation}
where $k$ is a constant characteristic of the aperture of the cone. Equation $(\ref{xproperty})$ says that the distance of a point from the cone's axis is in constant proportion to its distance along the axis. The value of $k$ can be calculated from any point on the cone. We will calculate $k$ from the projection and orthogonal projection of a point of tangency, $\vec{p}$, of the sphere and cone.

The vector $\vec{p} - \vec{l}$ is along a generatrix of the cone, so it is perpendicular to $\vec{p} - \vec{c}$, which points from the center of the sphere to the point of tangency. Therefore, a right triangle is formed by $\vec{p}$, $\vec{c}$, and $\vec{l}$, with $\vec{c}$ and $\vec{l}$ at the ends of the hypotenuse. The length $L=\|\vec{c}-\vec{l}\|$ can be calculated from the givens and the distance $r=\|\vec{p}-\vec{c}\|$ is a given. By the pythagorean theorem the length of the other leg is $L'=\|\vec{p}-\vec{l}\|=\sqrt{L^2-r^2}$.
\end{appendices}
